---
title: "hw2"
author: "Aldo Sanjoto"
date: "September 27, 2017"
output: html_document
---

####1a)
```{r} 
library("alr4")
data("stopping")
#head(stopping)
#??stopping
model = lm(formula = Distance ~ Speed, data = stopping)
summary(model)
par(mfrow=c(2,2))
plot(model, add.smooth = FALSE)
```
 
####1b) There is slightly a curvature in the Residuals vs Fitted plot however the points are not evenly distributed. Thus, mean function might not be appropriate.

####1c) There's no problem with the constant variance since in the Scale vs Location plot, trend is roughly flat (constant).

```{r}
model$fitted.values[which.max(model$residuals)]

model$fitted.values[which.min(model$residuals)]

residuals(model)
```

####1d) Largest residual: 60th value: 35.6078272, Smallest residual: 41st value: -25.4095174

```{r}
#hatvalues(model)
hatvalues(model)[which.max(hatvalues(model))]
```
####1e) 61th has the largest leverage value with 0.08967251

####1f) 60th value might be the outlier since it is the furthest from the other points in the plot.

```{r}
#cooks distance
which(cooks.distance(model) >= 1)
plot(cooks.distance(model), type = "h")
```


####1g) Based on the plot above, no value is greater than 1 thus no influential points. 

####2a)
```{r}
data("drugcost")
head(drugcost)
model2 = lm(formula = COST ~ RXPM + GS + RI + COPAY + AGE + F + MM, data = drugcost)
par(mfrow=c(2,2))
plot(model2, add.smooth = FALSE)

```

####2b) The trend is roughly flat in the Residual vs Fitted plot. Thus, mean function might be appropriate.

####2c) There's no problem with the constant variance since in the Scale vs Location plot, trend is roughly flat (constant).

```{r}
match(max(residuals(model2)), residuals(model2))
fitted.values(model2)[match(max(residuals(model2)), residuals(model2))]

match(min(residuals(model2)), residuals(model2))
fitted.values(model2)[match(min(residuals(model2)), residuals(model2))]

residuals(model2)
```
####2d) Largest residual: 29th value: 0.122522528, Smallest residual: 10th value: -0.142888039


```{r}
hatvalues(model2)[which.max(hatvalues(model2))]
```

####2e) DE has the largest leverage value with 0.6553194

####2f) DE is the outlier because it is the furthest from the other of the points in the plot.

```{r}
which(cooks.distance(model2) >= 1)
plot(cooks.distance(model2), type = "h")
```

####2g) Based on the plot above, there exist a value that is greater than 1 thus there is a influential point.


####3a)
```{r}
data("fuel2001")
head(fuel2001)
model3 = lm(formula = FuelC ~ Tax + Drivers + Income, data = fuel2001)
y = rstandard(model3)
x = model3$residuals
par(mfrow=c(1,1))
plot(x, y, xlab="ordinary residuals",ylab="standardized residuals")
            
```

####3b) Points in the plot do not exactly fall on a straightline indicates there might be an error in the independent and identically distributed normal. 

####3c)
```{r}
rstudent(model3)
```
```{r}
values = qt(0.05, df = df.residual(model3) - 1, lower = FALSE)
studentized = rstudent(model3)
which(abs(studentized) > values)
```
####3d) FL, NY, TX states are considered as outliers. 

```{r}
values2 = qt(0.05/(2*nobs(model3)), df = df.residual(model3) - 1, lower = FALSE)
which(abs(studentized) > values2)
```
####3e) NY, TX states are considered as outliers. 


####4a)
```{r}
par(pty = "s")
par(mfrow = c(3,3))
for(i in 1:9){qqnorm(rgeom(50,0.4))}
```

####4b) What makes the above plots different with normally-distributed data:
####First difference: The shape is kind of curvy.
####Second difference: All plots have gap between the points which means it is step graphs.
