---
title: "hw3 stat425"
author: "Aldo Sanjoto"
date: "October 13, 2017"
output: html_document
---

####1a)
```{r}
library("alr4")
data("MinnWater")
pairs(MinnWater)
#??Minnwater
```

####1b) Year, statePop, muniPop

####1c)
```{r}
fit_mw = lm(formula = muniUse ~ ., data = MinnWater)
summary(fit_mw)
```

```{r}
vif(fit_mw)
```

####1d) the variable year, allUse, irrUse, statePop, muniPop have a VIF indicating a possible problem.


```{r}
fit_mw2 = lm(formula = muniUse ~ allUse + irrUse + muniPrecip + statePop, data = MinnWater)
summary(fit_mw2)
```

####1e) Only the variable muniPrecip is not significant at level 5%

```{r}
vif(fit_mw2)
```

####1f) compared to the VIF in 1e, the VIF decreased. The variables muniPrecip and statePop have a VIF indicating a problem.

####2a)
```{r}
age = c(1, 2, 3, 4, 5)
number = c(123, 78, 32, 17, 24)
average_weight = c(7.9725, 7.9503, 7.9276, 7.8962, 7.8730)
std = c(0.01409, 0.02272, 0.03426, 0.04057, 0.05353)
money = data.frame(age, number, average_weight, std)
#View(money)
fit_money = lm(formula = average_weight ~ age, data = money)
summary(fit_money)

```

```{r}
confint(fit_money, "age")
```

####2b) the 95% confidence interval for the regression slope is -0.02820043 to -0.02241957

```{r}
fit_money2 = lm(formula = average_weight ~ age, data = money, weights = money$number)
summary(fit_money2)
```

```{r}
weight =  c(123, 78, 32, 17, 24)
w = diag(weight, ncol = 5, nrow = 5)

print("Weight matrix:")
print(w)

s = solve(w)
print("Sigma matrix:")
print(s)

```
####2d) The weight is a diagonal matrix with its element is equal to numbers respectively, the sigma matrix is the inverse of weight matrix 

```{r}
confint(fit_money2, "age")
```

####2e) the 95% confidence interval is from -0.0273745 to -0.02201086

####2f)
```{r}
fit_money3 = lm(formula = average_weight ~ age, data = money, weights = (money$number / (money$std^2)))
summary(fit_money3)
```
```{r}
weight2 = c(619559.6942, 151104.6915, 27263.10154, 10328.53929, 8375.615944)
w2 = diag(weight2, ncol = 5, nrow = 5)

print("Weight matrix:")
print(w2)

s2 = solve(w2)
print("Sigma matrix:")
print(s2)
```

####2g) The weight is a diagonal matrix with its element is equal to numbers/(std^2) respectively, the sigma matrix is the inverse of weight matrix 

```{r}
confint(fit_money3, "age")
```
####2h) the 95% confidence interval is from -0.02655593 to -0.02095642


####3a)
```{r}
data("lakemary")
#head(lakemary)
fit_lm = lm(formula = Length ~ Age, data = lakemary)
summary(fit_lm)
```

####3b)
```{r}
plot(lakemary$Age, lakemary$Length, xlab="Age (years)", ylab ="Length(mm)")
abline(fit_lm)
```

####3c) Because there are repeated data observation of the same number of Age.


```{r}
fit_lm_lof = lm(formula = Length ~ factor(Age), data = lakemary)
anova(fit_lm, fit_lm_lof)
```

####3d) from the lack-of-fit anova model, we can see that the pvalue 0.0002125 is really small so we decide to reject the null. Thus, the model is insufficient.

####3e) the estimate pure error variance is 8812.7/72 = 122.4

####3f)
```{r}
fit_lm2 = lm(formula = Length ~ Age + I(Age^2), data = lakemary)
summary(fit_lm2)
```

```{r}
anova(fit_lm2, fit_lm_lof)
```

####3g) from the lack-of-fit anova model, we can see that the pvalue 0.8295 is quite large so we fail to reject the null. Thus, the quadratic model is a sufficient model.
