---
title: "HW6 STAT425"
author: "Aldo Sanjoto"
date: "December 1, 2017"
output: html_document
---

####1a)
```{r}
bfhs = read.table("BFHS.dat", header = TRUE)
summary(bfhs)
```
```{r}
dif = bfhs$Intervention - bfhs$ExternalComparison
t.test(dif)

```

####1b) No significance difference between the intervention and external comparison as the p-value is greater than 0.05

```{r}
tstats = replicate(100000, t.test(dif * sample(c(-1,1),13,replace=TRUE))$statistic) 
tobserved = t.test(dif)$statistic 
approx_pval = mean(abs(tstats) >= abs(tobserved))
approx_pval
                  
```

####1c) There's a significant difference between the intervention and external comparison as the p-value is lesser than 0.05.

####1d)
```{r}
hist(tstats, main = "randomization distribution t-stat", freq = FALSE, breaks = 30, ylim = c(0, 0.5))
lines(seq(-4,4,len=100), dt(seq(-4,4,len=100), df = 5))
abline(v = c(tobserved,-tobserved), lty=2)
```


```{r}
barley = read.csv("Barley1928.csv")
table(barley$Block)
```

####2a) There are 5 blocks with a total of 30 experimental units.

####2b)
```{r}
barley$Treatment = as.factor(barley$Treatment)
fit = lm(formula = Yield ~ Block + Treatment, data = barley)
summary(fit)
```

```{r}
anova(fit)
```

####2c) Treatment effects are statistically significant because p-value < 0.05
  
####2d)
```{r}
TukeyHSD(aov(fit))$Treatment
```

####2e) Based on the Tukey intervals, 2-1, 3-1, 4-1, 5-1, 4-2, 5-2 are the pairs of treatments that have significantly different means

```{r}
spelling = read.csv("Spelling1941.csv")
```

####3a) the 2 blocking factors are "List" and "Group"

```{r}
matrix(spelling$Testing, nrow = 4, ncol = 4)
```

####3b) Column = List, Row = Group

####3c)
```{r}
fit_2 = lm(formula = Number ~ List + factor(Group) + Testing, data = spelling)
summary(fit_2)
```

```{r}
anova(fit_2)
```

####3d) Treatment effects are statistically significant because p-value < 0.05

####3e)
```{r}
TukeyHSD(aov(fit_2))$Testing
```

####3f) Based on the Tukey intervals, SD-MC, SW-MC, WS-MC  are the pairs of treatments that have significantly different means